%==========================================================================
% CV_Chunlei_Peng.tex
%
% Chunlei Peng
% Xidian University
% Written on July, 2015.
%
% Reference: http://www.tedpavlic.com/post_resume_cv_latex_example.php
%
% Any questions please contact: clp.xidian@gmail.com
%==========================================================================

%=========================== Document Setup ===============================
% Don't like 10pt? Try 11pt or 12pt
\documentclass[11pt]{article}
\RequirePackage[T1]{fontenc}
\usepackage{times}
\usepackage{calc}
\usepackage[shortcuts]{extdash}
\reversemarginpar

%% Use these lines for letter-sized paper
%\usepackage[paper=letterpaper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=1.2in,     % Length of section titles
%            marginparsep=.05in,       % Space between titles and text
%            margin=1in,               % 1 inch margins
%            includemp]{geometry}

%% Use these lines for A4-sized paper
\usepackage[paper=a4paper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=30.5mm,    % Length of section titles
            marginparsep=1.5mm,       % Space between titles and text
            margin=25mm,              % 25mm margins
            includemp]{geometry}

\setlength{\parindent}{0in}

\usepackage[shortlabels]{enumitem}
%   NOTICE: If you have trouble with "\restartlist{bibenum}",
%           please add the newest version of "enumitem.sty":
%           http://www.ctan.org/tex-archive/macros/latex/contrib/enumitem.
\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newlist{bibsection}{itemize}{3}
\setlist[bibsection]{label=,leftmargin=\bibhang,%
        itemindent=-\bibhang,
        itemsep=\bibsep,parsep=\z@,partopsep=0pt,
        topsep=0pt}
\newlist{bibenum}{enumerate}{3}
\setlist[bibenum]{label=[\arabic*],resume,leftmargin={\bibhang+\widthof{[999]}},%
        itemindent=-\bibhang,
        itemsep=\bibsep,parsep=\z@,partopsep=0pt,
        topsep=0pt}
\let\oldendbibenum\endbibenum
\def\endbibenum{\oldendbibenum\vspace{-.6\baselineskip}}
\let\oldendbibsection\endbibsection
\def\endbibsection{\oldendbibsection\vspace{-.6\baselineskip}}
\makeatother

\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

\newcommand{\makeheading}[2][]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
             {\large \bfseries #2 \hfill #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

\renewcommand{\section}[1]{\pagebreak[3]%
    \vspace{1.3\baselineskip}%
    \phantomsection\addcontentsline{toc}{section}{#1}%
    \noindent\llap{\scshape\smash{\parbox[t]{\marginparwidth}{\hyphenpenalty=10000\raggedright #1}}}%
    \vspace{-\baselineskip}\par}

\newcommand*\fixendlist[1]{%
    \expandafter\let\csname preFixEndListend#1\expandafter\endcsname\csname end#1\endcsname
    \expandafter\def\csname end#1\endcsname{\csname preFixEndListend#1\endcsname\vspace{-0.6\baselineskip}}}

\let\originalItem\item
\newcommand*\fixouterlist[1]{%
    \expandafter\let\csname preFixOuterList#1\expandafter\endcsname\csname #1\endcsname
    \expandafter\def\csname #1\endcsname{\let\oldItem\item\def\item{\pagebreak[2]\oldItem}\csname preFixOuterList#1\endcsname}
    \expandafter\let\csname preFixOuterListend#1\expandafter\endcsname\csname end#1\endcsname
    \expandafter\def\csname end#1\endcsname{\let\item\oldItem\csname preFixOuterListend#1\endcsname}}
\newcommand*\fixinnerlist[1]{%
    \expandafter\let\csname preFixInnerList#1\expandafter\endcsname\csname #1\endcsname
    \expandafter\def\csname #1\endcsname{\let\oldItem\item\let\item\originalItem\csname preFixInnerList#1\endcsname}
    \expandafter\let\csname preFixInnerListend#1\expandafter\endcsname\csname end#1\endcsname
    \expandafter\def\csname end#1\endcsname{\csname preFixInnerListend#1\endcsname\let\item\oldItem}}

\newlist{outerlist}{itemize}{3}
    \setlist[outerlist]{label=\enskip\textbullet,leftmargin=*}
    \fixendlist{outerlist}
    \fixouterlist{outerlist}

\newlist{lonelist}{itemize}{3}
    \setlist[lonelist]{label=\enskip\textbullet,leftmargin=*,partopsep=0pt,topsep=0pt}
    \fixendlist{lonelist}
    \fixouterlist{lonelist}

\newlist{innerlist}{itemize}{3}
    \setlist[innerlist]{label=\enskip\textbullet,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt}
    \fixinnerlist{innerlist}

\newlist{loneinnerlist}{itemize}{3}
    \setlist[loneinnerlist]{label=\enskip\textbullet,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt}
    \fixendlist{loneinnerlist}
    \fixinnerlist{loneinnerlist}

\newcommand{\blankline}{\quad\pagebreak[3]}
\newcommand{\halfblankline}{\quad\vspace{-0.5\baselineskip}\pagebreak[3]}

\usepackage{doi}
\usepackage{url}
\urlstyle{same}
\providecommand*\emaillink[1]{\nolinkurl{#1}}
\providecommand*\email[1]{\href{mailto:#1}{\emaillink{#1}}}
\providecommand\BibTeX{{B\kern-.05em{\sc i\kern-.025em b}\kern-.08em \TeX}}
\providecommand\Matlab{\textsc{Matlab}}
\hyphenation{bio-mim-ic-ry bio-in-spi-ra-tion re-us-a-ble pro-vid-er Media-Wiki}

%=========================== End Document Setup ==============================

\begin{document}
\makeheading{Chunlei Peng,\quad Ph.D. Candidate}

\section{Contact Information}

\newlength{\rcollength}\setlength{\rcollength}{1.85in}%
\newlength{\spacewidth}\setlength{\spacewidth}{20pt}
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength-\spacewidth}@{}p{\spacewidth}@{}p{\rcollength}}%

% Address box
\parbox{\textwidth-\rcollength-\spacewidth}{%
\href{http://see.xidian.edu.cn/vipsl/index.html}{VIPS Lab}\\
\href{http://isn.xidian.edu.cn/}{State Key Laboratory of ISN}\\
School of Electronic Engineering\\
Xidian University, No. 2 South Taibai Road\\
Xi'an, China, 710071}

&
% Uncomment to add a vertical bar in middle of contact information
%{\vrule width 0.5pt}
\parbox[m][5\baselineskip]{\spacewidth}{} &

% Non-snail-mail contact information
\parbox{\rcollength}{%
\textit{Phone:} +86 15829916976 \\
\textit{Email:} \email{clp.xidian@gmail.com}\\
\textit{Homepage:} \href{http://chunleipeng.com/}{http://chunleipeng.com/}}

\end{tabular}

\section{Research Interests}

Machine learning, computer vision, image processing, and pattern recognition with applications to \textbf{heterogeneous image transformation} (e.g. face sketch-photo synthesis) and \textbf{heterogeneous face recognition} (e.g. matching viewed/composite/forensic sketches to face photos, and matching near-infrared/thermal-infrared images to visible light face images).

\section{Education}

Sep. 2012 - Present

\begin{innerlist}
\item[] \textbf{Ph.D. Candidate} in Intelligent Information Processing
\item[] School of Electronic Engineering
\item[] Xidian University, Xi'an, China
\item[] Adviser: \href{http://see.xidian.edu.cn/faculty/xbgao/}{Xinbo Gao}
\end{innerlist}

\halfblankline

Sep. 2008 - July 2012

\begin{innerlist}
\item[] \textbf{Bachelor} in Electronical and Information Engineering
\item[] School of Electronic Engineering
\item[] Xidian University, Xi'an, China
\item[] Undergraduate thesis: ``Adaptive Markov Random Field based Face Sketch-Photo Synthesis'' (\emph{Outstanding undergraduate thesis})
\item[] Rank: 6/543
\end{innerlist}

\section{Research Experiences}

\begin{innerlist}

\item \textbf{Multimedia Information Processing and Analysis}, supported by the National Natural Science Foundation of China (Grant No. 61125204), participant, 2012.01-2015.12

\halfblankline

\item \textbf{Generalized Sparse Representation based Heterogeneous Face Image Transformation and Quality Assessment}, supported by National Natural Science Foundation of China (Grant No.61172146), participant, 2012.01-2015.12

\halfblankline

\item \textbf{Heterogeneous Image Transformation and Quality Assessment}, supported by the Fundamental Research Funds for the Central Universities (Grant No. JB149901), participant, 2014.01-2015.12

\halfblankline

\item \textbf{On Cross Media Heterogeneous Image Transformation and Recognition based on Big Data}, Transverse Research Projects, participant, 2013.11-2015.04

\halfblankline

\item \textbf{Transductive Learning based Heterogeneous Face Image Transformation from An Arbitrary Profile}, supported by the Fundamental Research Funds for the Central Universities (Grant No. K50513100009), participant, 2013.01-2013.12

\end{innerlist}

\section{Publications}

\textbf{Journals}

\vspace{0.1in}

\begin{bibenum}
\item \textbf{Chunlei Peng}, Xinbo Gao, Nannan Wang, and Jie Li, "Graphical Representation for Heterogeneous Face Recognition," \emph{IEEE Transactions on Pattern Analysis and Machine Intelligence (\textbf{IEEE TPAMI})}, Accepted, 2016.
    (\emph{Graphical representations are obtained through Markov networks, with spatial information taken into consideration. Leading performance is achieved on multiple heterogeneous face recognition scenarios.})

\item \textbf{Chunlei Peng}, Xinbo Gao, Nannan Wang, Dacheng Tao, Xuelong Li, and Jie Li, ``Multiple Representations based Face Sketch-Photo Synthesis,'' \emph{IEEE Transactions on Neural Networks and Learning Systems (\textbf{IEEE TNNLS})}, Accepted, 2015.
    (\emph{We adaptively learn the combination weights of multiple representations, and the synthesis process is robust to different lighting conditions and backgrounds on real-world forensic sketches and mug shots.})

\item \textbf{Chunlei Peng}, Xinbo Gao, Nannan Wang, Jie Li, "Superpixel-based Face Sketch-Photo Synthesis," \emph{IEEE Transactions on Circuits and Systems for Video Technology (\textbf{IEEE TCSVT})}, Accepted, 2015.
    (\emph{Superpixel is firstly introduced into face sketch-photo synthesis scenario, which can take inherent face structure into consideration.})

\item \textbf{Chunlei Peng}, Xinbo Gao, Nannan Wang, and Jie Li, "Sparse Graphical Representation based Discriminant Analysis for Heterogeneous Face Recognition," \emph{IEEE Transactions on Cybernetics (\textbf{IEEE TC})}, Under Review, 2015.
    (\emph{Adaptive sparse graphical representations are obtained. We further develop a spatial partition-based discriminant analysis framework including row-based, column-based, and learning-based strategies.})

\item Xinbo Gao, Nannan Wang, \textbf{Chunlei Peng}, and Chengyuan Li, "Triple Space Fusion based Face Image Recognition," \emph{Pattern Recognition and Artificial Intelligence}, vol. 28, no. 9, pp. 811-821, 2015. (Invited, in Chinese)
    (\emph{Review the recent advances on heterogeneous face recognition based on triple space fusion, i.e. the fusion of the physical space, the information space, and the cognitive space.})

\end{bibenum}

\vspace{0.2in}

\restartlist{bibenum}

\textbf{Conference}

\vspace{0.1in}

\begin{bibenum}
\item \textbf{Chunlei Peng}, Jie Li, Nannan Wang, and Xinbo Gao, "Multi-View Representation based Face Sketch Synthesis," \emph{ACM International Conference on Internet Multimedia Computing and Service (\textbf{ICIMCS})}, 2014, pp. 307-312.

\item Xinye Yu, Nannan Wang, \textbf{Chunlei Peng}, Jie Li, and Xinbo Gao, "Adaptive Representation-based Face Sketch Synthesis," \emph{International Conference on Intelligence Science and Big Data Engineering (\textbf{IScIDE})}, Accepted, 2016.

\end{bibenum}

\vspace{0.2in}

\restartlist{bibenum}

\textbf{Book Chapter}

\vspace{0.1in}

\begin{bibenum}
\item Nannan Wang, Shengchuan Zhang, \textbf{Chunlei Peng}, Jie Li, and Xinbo Gao, "Face Sketch Recognition via Data-driven Synthesis," \emph{Biometrics in Forensic Science}, Springer, 2015.

\end{bibenum}

\vspace{0.2in}

\restartlist{bibenum}

\section{Patents}

\begin{bibenum}

\item Xinbo Gao, \textbf{Chunlei Peng}, et al., "Forensic Sketch based Face Recognition," \emph{Chinese Patent Pending}, No. 201410166300.7, 2014.

\item Jie Li, \textbf{Chunlei Peng}, et al., "Multiple Features Fusion based Image Synthesis," \emph{Chinese Patent Pending}, No. 201410165469.0, 2014.

\item Xinbo Gao, \textbf{Chunlei Peng}, et al., "Graphical Representation based Face Sketch-Photo Recognition," \emph{Chinese Patent Pending}, No. 201510397326.7, 2015.

\item Xinbo Gao, \textbf{Chunlei Peng}, et al., "Superpixel based Face Sketch Synthesis," \emph{Chinese Patent Pending}, No. 201510395890.5, 2015.

\item Xinbo Gao, Wenjun Ren, Nannan Wang, Jie Li, \textbf{Chunlei Peng}, et al., "Image Quality Assessment based Synthesized Face Image Recognition," \emph{Chinese Patent Pending}, No. 201410133868.9, 2014.

\item Xinbo Gao, Yanting Hu, Nannan Wang, Jie Li, Wenjun Ren, \textbf{Chunlei Peng}, et al., "Cascade Linear Regression based Image Super-Resolution", \emph{Chinese Patent Pending}, No. 201410766467.7, 2014.

\item Jie Li, Mingjin Zhang, Xinbo Gao, Nannan Wang, Shengchuan Zhang, \textbf{Chunlei Peng}, et al., "Support Vector Machine based Sketch Style Classification," \emph{Chinese Patent Pending}, No. 201410330945.X, 2014.

\item Xinbo Gao, Shengchuan Zhang, Nannan Wang, Jie Li, Mingjin Zhang, Yanting Hu, \textbf{Chunlei Peng}, and Wenjun Ren, "Greedy Search based Face Sketch Synthesis," \emph{Chinese Patent Pending}, No. 201410818175.3, 2014.

\item Xinbo Gao, Nannan Wang, Wenjun Ren, Jie Li, Yanting Hu, Shengchuan Zhang, Mingjin Zhang, and \textbf{Chunlei Peng}, "Feature Similarity based Synthesized Face Sketch Quality Assessment," \emph{Chinese Patent Pending}, No. 201410771613.5, 2014.

\item Nannan Wang, Xinbo Gao, Shengchuan Zhang, Jie Li, Feng Wang, Xinye Yu, Mingjin Zhang, \textbf{Chunlei Peng}, and Yanting Hu, "One Target Sketch based Face Sketch Synthesis," \emph{Chinese Patent Pending}, No. 201510109196.2, 2015.

\item Nannan Wang, Xinbo Gao, Shengchuan Zhang, Jie Li, Feng Wang, Xinye Yu, Mingjin Zhang, \textbf{Chunlei Peng}, and Yanting Hu, "Single Photo-Sketch Pair based Face Sketch Synthesis," \emph{Chinese Patent Pending}, No. 201510109027.9, 2015.

\end{bibenum}

\section{Awards}

Outstanding Graduate Student, Xidian University \hfill 2014

\vspace{0.1in}
First-Class Graduate Scholarship for PhD candidate, Xidian University \hfill 2014

\vspace{0.1in}
Second-Class Graduate Scholarship for PhD candidate, Xidian University \hfill 2013

\vspace{0.1in}
Outstanding Undergraduate Thesis, Xidian University \hfill 2012

\vspace{0.1in}
Third Prize in ACM-ICPC, Xidian University \hfill 2011

\vspace{0.1in}
Outstanding Student, Xidian University \hfill 2009

\section{Professional Activity}

Review for \textbf{Neurocomputing} (Elsevier) from 2015;

\vspace{0.1in}
Review for \textbf{27th IEEE International Conference on Tools with Artificial Intelligence (ICTAI)}, Vietri sul Mare, Italy, November, 2015.

\section{Skills}

Proficient in Matlab, C/C++, Qt, OpenCV, Latex; Familiar with Python, Java

\end{document}

%----------------------------------------------------------------------%
% The following is copyright and licensing information for
% redistribution of this LaTeX source code; it also includes a liability
% statement. If this source code is not being redistributed to others,
% it may be omitted. It has no effect on the function of the above code.
%----------------------------------------------------------------------%
% Copyright (c) 2007, 2008, 2009, 2010, 2011 by Theodore P. Pavlic
%
% Unless otherwise expressly stated, this work is licensed under the
% Creative Commons Attribution-Noncommercial 3.0 United States License. To
% view a copy of this license, visit
% http://creativecommons.org/licenses/by-nc/3.0/us/ or send a letter to
% Creative Commons, 171 Second Street, Suite 300, San Francisco,
% California, 94105, USA.
%
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS
% OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
% MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT.
% IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY
% CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT,
% TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE
% SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
%----------------------------------------------------------------------%
